Global SOC maps and emissions

### 2022-07-20 ResultNotebooks/results_SOCcompare.Rmd
update of output scripts and figure

---
title: "SOC budget analysis in comparsion"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

@@

rev        <- "rev30"

outputdir  <- "Output/"

SoilCarbon <- read.magpie(paste0("Data/", rev, "histManagement/SoilCarbon.rds"))
Landuse    <- read.magpie(paste0("Data/", rev, "histManagement/Landuse.rds"))

```

@@

SoilCarbon[,,c("naturalstate.crop")] <- SoilCarbon[,,c("naturalstate.natveg")]
SOCStock     <- dimSums(dimSums(SoilCarbon[,,c("naturalstate","actualstate")], dim=3.3)* Landuse, dim=3.2)
cell2reg     <- read.csv("Data/additional/ClimateZoneMapping.csv")
reg_SOCStock <- toolAggregate(SOCStock, rel=cell2reg, from="cell", to="IPCC")
```

@@

SOCStock <- reg_SOCStock
reg_SOC  <- mbind(setNames(SOCStock[,"y2010","actualstate"],"This Study"),
                  setNames(SOCStock[,"y2010","naturalstate"],"This Study (PNV)"),
                  setNames(LPJmL4[,"y2010",], "LPJmL4"),
                  setYears(setNames(WISE[,1,],"WISE"), "y2010"),
                  setYears(setNames(SoilGrids[,1,],"SoilGrids"),"y2010"),
                  setYears(setNames(GSOC[,1,],"GSOC"),"y2010"),
                  setYears(setNames(SoilGrids2[,1,],"SoilGrids2"),"y2010"),
                  setYears(setNames(SOCDebtPaper[,"y2010",],"SOCDebtPaper"),"y2010"))
glo_SOC <- mbind(setCells(dimSums(reg_SOC, dim=1),"GLO"), reg_SOC)

#print(dimOrder(comparison[,,sort(getNames(comparison,dim=1))], c(2,1)))

comparison_table  <- data.frame(dcast(as.data.frame(collapseNames(glo_SOC/1000)), 
                           Data1 ~ Region, value.var="Value", 
                            row.names=levels(as.data.frame(glo_SOC)$Data1)))

@@

saveRDS(object = comparison_table, paste0(outputdir,"gloSOC_comparison.rds"))

```

@@

names(table) <- c("Data1","Boreal Dry", "Boreal Moist", "C-Temp Dry", "C-Temp Moist","GLO","Polar Dry", "Polar Moist",
                  "Tropical Dry", "Tropical Moist", "Tropical Montane", "Tropical Wet", "W-Temp Dry", "W-Temp Moist", "Year")
table        <- table[,c(1,15,6,7,8,2,3,4,5,13,14,9,10,11,12)]

cols   <-c("black",   "#DF536B", "#61D04F", "#2297E6",
           "#28E2E5", "#CD0BBC", "#F5C710", "gray62")[c(2, 7, 1, 3, 4, 5, 6, 8)]

glob <- ggplot(data = melt(subset(table, select =c(Data1, GLO, Year))), aes(y=Year,x=value, group=Data1)) + 
  geom_point(aes(colour=Data1, size=Data1, shape=Data1)) + 
  scale_size_manual( values = c( 4,  2, 2, 2, 2, 2, 2,  2)) + 
  scale_shape_manual(values = c(19, 16, 6, 2, 5, 0, 8, 10)) +
  scale_color_manual(values = cols) +
  labs(color  = leg_name, size = leg_name, shape = leg_name) +
  ylab("") + xlab("SOC (0-30cm) in GtC") +
  theme(axis.ticks.y =element_blank(),
        axis.text.y=element_blank(), 
        legend.position="bottom") + 
  guides(fill=guide_legend(nrow=2, byrow=TRUE))
        #legend.position="right") + guides(fill=guide_legend(ncol=1,byrow=TRUE))

comp <- ggplot(data = melt(subset(table, select=-GLO)), aes(y=Year,x=value, group=Data1)) + 
  geom_point(aes(colour=Data1, size=Data1, shape=Data1)) + 
  facet_wrap(~ variable, scales="free", drop=TRUE, labeller = label_wrap_gen(width=18)) + 
  scale_size_manual( values = c( 4,  2, 2, 2, 2, 2, 2,  2)) + 
  scale_shape_manual(values = c(19, 16, 6, 2, 5, 0, 8, 10)) +
  scale_color_manual(values = cols) +
  labs(color  = leg_name, size = leg_name, shape = leg_name) +
  ylab("") + xlab("SOC (0-30cm) in GtC") +
  theme(axis.ticks.y=element_blank(),
        axis.text.y=element_blank(),
        legend.position = "bottom") + guides(fill=guide_legend(nrow=2,byrow=TRUE))

@@

ggsave(paste0(outputdir,"/Images/glo_comparisonfigure.png"), plot=glob, height=4, width=10, units="cm", dpi = 300)
ggsave(paste0(outputdir,"/Images/reg_comparisonfigure.png"), plot=comp, height=9, width=15, units="cm", dpi = 300)

```

@@

glob
ggsave(paste0(outputdir,"/glo_comparisonfigure.png"), plot=glob)
```
`

>>>>

---
title: "SOC budget analysis in comparsion to other global SOC estimates"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

@@

rev        <- "rev30"
outputdir  <- "Output/"

SoilCarbon <- read.magpie(paste0("Data/", rev, "histManagement/SoilCarbon.rds"))
Landuse    <- read.magpie(paste0("Data/", rev, "histManagement/Landuse.rds"))
```

@@

SoilCarbon[, , c("naturalstate.crop")] <- SoilCarbon[, , c("naturalstate.natveg")]
SOCStock     <- dimSums(dimSums(SoilCarbon[, , c("naturalstate", "actualstate")],
                                dim = 3.3) * Landuse, dim = 3.2)
cell2reg     <- read.csv("Data/additional/ClimateZoneMapping.csv")
reg_SOCStock <- toolAggregate(SOCStock, rel = cell2reg, from = "cell", to = "IPCC")
```

@@

SOCStock <- reg_SOCStock
reg_SOC  <-
  mbind(setNames(SOCStock[, "y2010", "actualstate"], "This Study"),
        setNames(SOCStock[, "y2010", "naturalstate"], "This Study (PNV)"),
        setNames(LPJmL4[, "y2010", ], "LPJmL4"),
        setYears(setNames(WISE[, 1, ], "WISE"), "y2010"),
        setYears(setNames(SoilGrids[, 1, ], "SoilGrids"), "y2010"),
        setYears(setNames(GSOC[, 1, ], "GSOC"), "y2010"),
        setYears(setNames(SoilGrids2[, 1, ], "SoilGrids 2.0"), "y2010"),
        setYears(setNames(SOCDebtPaper[, "y2010", ], "SOCDebtPaper"), "y2010"))
glo_SOC <- mbind(setCells(dimSums(reg_SOC, dim = 1), "GLO"), reg_SOC)

# print(dimOrder(comparison[,,sort(getNames(comparison,dim=1))], c(2,1)))

comparison_table  <- data.frame(dcast(as.data.frame(collapseNames(glo_SOC / 1000)),
                           Data1 ~ Region, value.var = "Value",
                            row.names = levels(as.data.frame(glo_SOC)$Data1)))

@@

saveRDS(object = comparison_table, paste0(outputdir, "gloSOC_comparison.rds"))
```

@@

names(table) <- c("Data1", "Boreal Dry", "Boreal Moist", "C-Temp Dry",
                  "C-Temp Moist", "GLO", "Polar Dry", "Polar Moist",
                  "Tropical Dry", "Tropical Moist", "Tropical Montane",
                  "Tropical Wet", "W-Temp Dry", "W-Temp Moist", "Year")
table        <- table[, c(1, 15, 6, 7, 8, 2, 3, 4, 5, 13, 14, 9, 10, 11, 12)]

cols   <- c("black",   "#DF536B", "#61D04F",
           "#2297E6", "#28E2E5", "#CD0BBC",
           "#F5C710", "gray62")[c(2, 7, 1, 3, 4, 5, 6, 8)]

glob <- ggplot(data = melt(subset(table, select = c(Data1, GLO, Year))),
               aes(x = Year, y = value, group = Data1)) +
  geom_point(aes(colour = Data1, size = Data1, shape = Data1)) +
  scale_size_manual(values = c(4,  2, 2, 2, 2, 2, 2,  2)) +
  scale_shape_manual(values = c(19, 16, 6, 2, 5, 0, 8, 10)) +
  scale_color_manual(values = cols) +
  labs(color  = leg_name, size = leg_name, shape = leg_name) +
  xlab("") + ylab("SOC (0-30cm) in GtC") +
  theme(axis.ticks.x = element_blank(),
        axis.text.x  = element_blank(),
        legend.position = "right")

comp <- ggplot(data = melt(subset(table, select = -GLO)),
               aes(x = Year, y = value, group = Data1)) +
  geom_point(aes(colour = Data1, size = Data1, shape = Data1)) +
  facet_wrap(~variable, scales = "free", drop = TRUE,
             labeller = label_wrap_gen(width = 18)) +
  scale_size_manual(values = c(4,  2, 2, 2, 2, 2, 2,  2)) +
  scale_shape_manual(values = c(19, 16, 6, 2, 5, 0, 8, 10)) +
  scale_color_manual(values = cols) +
  labs(color  = leg_name, size = leg_name, shape = leg_name) +
  xlab("") + ylab("SOC (0-30cm) in GtC") +
  theme(axis.ticks.x = element_blank(),
        axis.text.x  = element_blank(),
        legend.position = "bottom") +
  guides(fill = guide_legend(nrow = 3, byrow = TRUE))

@@

ggsave(paste0(outputdir, "/Images/glo_comparisonfigure.png"),
       plot = glob, height =  7, width =  7, units = "cm", dpi = 300)
ggsave(paste0(outputdir, "/Images/reg_comparisonfigure.png"),
       plot = comp, height = 15, width = 14, units = "cm", dpi = 300)
```

@@

glob
ggsave(paste0(outputdir, "/glo_comparisonfigure.png"), plot = glob)
```
`

### 2022-07-20 ResultNotebooks/results_SOCmaps.Rmd
update of output scripts and figure

rev <- "rev30"

filesNeeded <- c("SoilCarbon.rds","Landuse.rds")

scenarios    <- c("histManagement")#,"constManagement-1975", "constTillage-mixedtill", "constResidues-1975", "constManure-1975",
                  #"constManagement2-1975", "constResrate-1975", "constYield-1975",
                 #"Initial-natveg", "Initial-natveg_constManangement-1975", "Initial-natveg_constManangement2-1975", 
                 #"LitterPNV-PerennialGrasses", "LitterPNV-AASS", "LitterPNV-BRCF", 
                 #"LitterPNV-MTCF", "LitterPNV-BLEAF",  "LitterPNV-TREF")

# for(item in scenarios){
#    dir.create(path=paste0("Data/",paste0(rev,item)))
#    untar(paste0("Data/", paste0(rev,item), "_h12_carbonbudget.tgz"),
#    exdir=paste0("Data/", paste0(rev,item)), extras="--keep-newer-files ") # files=filesNeeded,
# }

outputdir <- "Output/Images"

SoilCarbon <- read.magpie(paste0("Data/",rev,scenarios[1],"/SoilCarbon.rds"))
Landuse    <- read.magpie(paste0("Data/",rev,scenarios[1],"/Landuse.rds"))

```

@@

years <- seq(1975,2010,1)

SoilCarbon[,,"naturalstate.crop"] <- SoilCarbon[,,"naturalstate.natveg"]
SOCStock        <- dimSums(dimSums(SoilCarbon[,years,][,,"state",pmatch=TRUE], dim=3.3)* Landuse[,years,], dim=3.2)
glo_SOCStock    <- dimSums(SOCStock, dim=1) 
glo_SOCEmission <- (glo_SOCStock[,,"naturalstate"] - glo_SOCStock[,,"actualstate"])/1000

cropland_dens    <- dimSums(SoilCarbon[,,"actualstate"][,,"crop"], dim=3)
cropland_dens[Landuse[,,"crop"] <= 0.001] <- NA

cropland_share <- dimSums(SoilCarbon[,,"actualstate"][,,"crop"], dim=3)/(dimSums(SoilCarbon[,,"naturalstate"][,,"natveg"], dim=3) + 1e-8)
cropland_share[Landuse[,,"crop"] <= 0.001] <- NA

cropland_increase <- dimSums(SoilCarbon[,,"actualstate"][,,"crop"], dim=3)-dimSums(SoilCarbon[,,"actualstate"][,,"natveg"], dim=3) 
cropland_increase[Landuse[,,"crop"] <= 0.001] <- NA

magpie_coord  <- toolGetMapping("magpie_coord.rda", type="cell")
share2plot    <- merge(as.data.frame(cropland_share), data.frame(magpie_coord, Cell=c(1:59199)), by="Cell")
increase2plot <- merge(as.data.frame(cropland_increase), data.frame(magpie_coord, Cell=c(1:59199)), by="Cell")
density2plot  <- merge(as.data.frame(cropland_dens), data.frame(magpie_coord, Cell=c(1:59199)), by="Cell")

```

@@

map.world <- map_data("world")
world         <- ne_countries(scale = "medium", returnclass = "sf")
data(coastlineWorld)  
coastline.world <- data.frame(longitude=coastlineWorld[["longitude"]],latitude=coastlineWorld[["latitude"]])

@@

  trans <- function(x) {
    if (any(is.na(x))) return(x)
    # get indices for the relevant regions
    isq <- x > from & x < to
    ito <- x >= to
    # apply transformation
    x[isq] <- from + (x[isq] - from)/factor
    x[ito] <- from + (to - from)/factor + (x[ito] - to)
    return(x)
  }

  inv <- function(x) {
    if (any(is.na(x))) return(x)
    # get indices for the relevant regions
    isq <- x > from & x < from + (to - from)/factor
    ito <- x >= from + (to - from)/factor
    # apply transformation
    x[isq] <- from + (x[isq] - from) * factor
    x[ito] <- to + (x[ito] - (from + (to - from)/factor))
    return(x)
  }
  # return the transformation
  return(trans_new("squished", trans, inv))
}

SOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCEmission)[,c(3,6)],  aes(x = Year, y = Value, group=1)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC'))) +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(trans = squish_trans(-34,0,10),
                     limits = c(-40,0),
                     breaks = c(0, -34, -35, -36, -37, -38, -39, -40),
                     minor_breaks = seq(-1,-29,-2)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 10, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size)#,
        #plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
        ) +
  annotate(geom="text", label="SOC debt", x=factor(1995), y=-20, size = 3) +
  annotate("segment", x = factor(1990), xend = factor(1990), y = 0, yend = -36, arrow=arrow(end="both", type="closed", length=unit(0.1, "inches")))

@@

  out <- ggplot(data = world) + geom_sf() + 
    geom_tile(data = subset(data, Year == "2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits   = limits, 
                      colours  = cols, 
                      name     = name,
                      values   = values,
                      breaks   = breaks,
                      labels   = labels, 
                      na.value = "white",
                      guide    = guide_legend(
                        title.theme    = element_text(size=legend_size),
                        direction      = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust    = 0.5,
                        label.hjust    = 1,
                        nrow           = 1,
                        byrow          = F,
                        label.position = "bottom",
                        keyheight      = 0.5,
                        keywidth       = 2
                      )) +
    theme(legend.position = "bottom",
          axis.title.x     = element_blank(), 
          axis.title.y     = element_blank(),
          legend.text      = element_text(size = legend_size),
          rect             = element_blank(),
          panel.background = element_rect(fill = "#F8F8FF", size = c(0.7,0.7)),
          plot.margin      = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )

@@

cols        <- colorRampPalette(brewer.pal(11, "RdYlBu"))(11)[c(1:6,7,9,11)]
SOCshare    <- SOCplotmap( data     = share2plot,
                            limits   = c(0,2),
                            cols     = cols,
                            name     = expression("cropland SOC stock change factor (unitless)"),
                            values   = c(0,0.2,0.4,0.6,0.8,1.0,1.2,2)/2,
                            breaks   = c(0.2,0.4,0.6,0.8,1.0,1.2,2),
                            labels   = c("< 0.2","0.4", "0.6","0.8","1.0","1.2","> 1.2"))

SOCincrease <- SOCplotmap( data     = increase2plot,
                            limits   = c(-100, 100),
                            cols     = cols,
                            name     = expression(paste('cropland \u0394SOC in tons of carbon per hectare')),
                            values   = (c(-100, -40, -30, -20, -10, 0, 10, 100)+100)/200,
                            breaks   =  c(-40, -30, -20, -10, 0, 10, 100),
                            labels   = c("< -40", "        -30","        -20","      -10 ","     0","    10","> 10"))

cols <- colorRampPalette(brewer.pal(9, "YlGn"))(8)[2:8]
SOCdensity  <- SOCplotmap( data     = density2plot,
                            limits   = c(0, 150), 
                            cols     = cols, 
                            name     = expression("cropland SOC in tons of carbon per hectare"), 
                            values   = c(0, 5, 10, 20, 40, 70, 100, 150) / 150,
                            breaks   = c(5, 10, 20, 40, 70, 100, 150),
                            labels   = c("0     5","  10","  20","  40","  70","  100"," >150"))

library(gridExtra)
library(cowplot)
SOCemis
SOCincrease
SOCdensity
SOCshare

grid <- plot_grid(SOCemis,SOCdensity,SOCincrease, SOCshare,  ncol=2, labels=c("(a)","(b)", "(c)", "(d)"),
                  label_fontface = "plain", label_size = 10)
grid
ggsave(paste0(outputdir,"/4panelfigure.png"), plot=grid, width = 20, height = 14, dpi = 300, units = "cm")
ggsave(paste0(outputdir,"/SOCshare.png"),    plot=SOCshare,    width = 10, height = 7, dpi = 300, units = "cm")
ggsave(paste0(outputdir,"/SOCincrease.png"), plot=SOCincrease, width = 10, height = 7, dpi = 300, units = "cm")
ggsave(paste0(outputdir,"/SOCdensity.png"),  plot=SOCdensity,  width = 10, height = 7, dpi = 300, units = "cm")
ggsave(paste0(outputdir,"/SOCemis.png"),     plot=SOCemis,     width = 10, height = 7, dpi = 300, units = "cm")

```

>>>>

rev         <- "rev30"
filesNeeded <- c("SoilCarbon.rds", "Landuse.rds")
scenarios   <- c("histManagement")
outputdir   <- "Output/Images"

SoilCarbon <- read.magpie(paste0("Data/", rev, scenarios[1], "/SoilCarbon.rds"))
Landuse    <- read.magpie(paste0("Data/", rev, scenarios[1], "/Landuse.rds"))
```

@@

years <- seq(1975, 2010, 1)

SoilCarbon[, , "naturalstate.crop"] <- SoilCarbon[, , "naturalstate.natveg"]
SOCStock        <- dimSums(
                     dimSums(
                       SoilCarbon[, years, ][, , "state", pmatch = TRUE],
                       dim = 3.3) *
                     Landuse[, years, ],
                     dim = 3.2)
glo_SOCStock    <- dimSums(SOCStock, dim = 1)
glo_SOCEmission <- (glo_SOCStock[, , "naturalstate"] -
                      glo_SOCStock[, , "actualstate"]) / 1000

cropland_dens   <- dimSums(SoilCarbon[, , "actualstate"][, , "crop"], dim = 3)
cropland_dens[Landuse[, , "crop"] <= 0.001] <- NA

cropland_share <- dimSums(SoilCarbon[, , "actualstate"][, , "crop"],
                          dim = 3) /
                 (dimSums(SoilCarbon[, , "naturalstate"][, , "natveg"],
                          dim = 3) + 1e-8)
cropland_share[Landuse[, , "crop"] <= 0.001] <- NA

cropland_increase <- dimSums(SoilCarbon[, , "actualstate"][, , "crop"],
                             dim = 3) -
                     dimSums(SoilCarbon[, , "naturalstate"][, , "natveg"],
                             dim = 3)
cropland_increase[Landuse[, , "crop"] <= 0.001] <- NA

magpie_coord  <- toolGetMapping("magpie_coord.rda", type = "cell")
share2plot    <- merge(as.data.frame(cropland_share),
                       data.frame(magpie_coord, Cell = c(1:59199)), by = "Cell")
increase2plot <- merge(as.data.frame(cropland_increase),
                       data.frame(magpie_coord, Cell = c(1:59199)), by = "Cell")
density2plot  <- merge(as.data.frame(cropland_dens),
                       data.frame(magpie_coord, Cell = c(1:59199)), by = "Cell")
```

@@

map.world <- map_data("world")
world     <- ne_countries(scale = "medium", returnclass = "sf")
data(coastlineWorld)
coastline.world <- data.frame(longitude = coastlineWorld[["longitude"]],
                              latitude  = coastlineWorld[["latitude"]])

@@

  trans <- function(x) {
    if (any(is.na(x))) return(x)
    # get indices for the relevant regions
    isq <- x > from & x < to
    ito <- x >= to
    # apply transformation
    x[isq] <- from + (x[isq] - from) / factor
    x[ito] <- from + (to - from) / factor + (x[ito] - to)
    return(x)
  }

  inv <- function(x) {
    if (any(is.na(x))) return(x)
    # get indices for the relevant regions
    isq <- x > from & x < from + (to - from) / factor
    ito <- x >= from + (to - from) / factor
    # apply transformation
    x[isq] <- from + (x[isq] - from) * factor
    x[ito] <- to + (x[ito] - (from + (to - from) / factor))
    return(x)
  }
  # return the transformation
  return(trans_new("squished", trans, inv))
}

SOCemis <- ggplot() +
  geom_line(data = as.data.frame(-glo_SOCEmission)[, c(3, 6)],
            aes(x = Year, y = Value, group = 1)) +
  labs(x = "Year",
        y = expression(paste("Global \u0394SOC in GtC"))) +
  scale_x_discrete(breaks = seq(1975, 2010, 5)) +
  scale_y_continuous(trans = squish_trans(-34, 0, 10),
                     limits = c(-40, 0),
                     breaks = c(0, -34, -35, -36, -37, -38, -39, -40),
                     minor_breaks = seq(-1, -29, -2)) +
  theme(rect = element_blank(),
        axis.title.y = element_text(size = legend_size),
        axis.title.x = element_text(size = legend_size,
                                    margin = margin(t = 10,
                                                    r = 0,
                                                    b = 10,
                                                    l = 0,
                                                   unit = "pt")),
        axis.text.x = element_text(angle = 60, hjust = 0.8, vjust = 0.8,
                                   size = legend_size)
        ) +
  annotate(geom = "text", label = "SOC debt",
           x = factor(1995), y = -20, size = 3) +
  annotate("segment", x = factor(1990), xend = factor(1990), y = 0, yend = -36,
           arrow = arrow(end    = "both",
                         type   = "closed",
                         length = unit(0.1, "inches")))

@@

  out <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(data, Year == "2010", c("lon", "lat", "Value")),
              aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits   = limits,
                      colours  = cols,
                      name     = name,
                      values   = values,
                      breaks   = breaks,
                      labels   = labels,
                      na.value = "white",
                      guide    = guide_legend(
                        title.theme    = element_text(size = legend_size),
                        direction      = "horizontal",
                        title.position = "top",
                        # I shift the labels around, the should be placed
                        # exactly at the right end of each legend key
                        title.hjust    = 0.5,
                        label.hjust    = 1,
                        nrow           = 1,
                        byrow          = FALSE,
                        label.position = "bottom",
                        keyheight      = 0.5,
                        keywidth       = 2
                      )) +
    theme(legend.position = "bottom",
          axis.title.x     = element_blank(),
          axis.title.y     = element_blank(),
          legend.text      = element_text(size = legend_size),
          rect             = element_blank(),
          panel.background = element_rect(fill = "#F8F8FF", size = c(0.7, 0.7)),
          plot.margin      = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )

@@

cols        <- colorRampPalette(brewer.pal(11, "RdYlBu"))(11)[c(1:6, 7, 9, 11)]
SOCshare    <-
  SOCplotmap(
    data     = share2plot,
    limits   = c(0, 2),
    cols     = cols,
    name     = expression("cropland SOC stock change factor (unitless)"),
    values   = c(0, 0.2, 0.4, 0.6, 0.8, 1.0, 1.2, 2) / 2,
    breaks   = c(0.2, 0.4, 0.6, 0.8, 1.0, 1.2, 2),
    labels   = c("< 0.2", "0.4", "0.6", "0.8", "1.0", "1.2", "> 1.2"))

SOCincrease <-
  SOCplotmap(
    data     = increase2plot,
    limits   = c(-100, 100),
    cols     = cols,
    name     = expression(
                 paste("cropland \u0394SOC in tons of carbon per hectare")),
    values   = (c(-100, -40, -30, -20, -10, 0, 10, 100) + 100) / 200,
    breaks   =  c(-40, -30, -20, -10, 0, 10, 100),
    labels   =  c("< -40", "        -30", "        -20",
                  "      -10 ", "     0", "    10", "> 10"))

cols <-
  colorRampPalette(
    c("white",
      brewer.pal(9, "YlGn")[c(1:2)],
      "yellow",
      brewer.pal(9, "YlGn")[c(4:7)],
      brewer.pal(9, "YlGnBu")[c(6:9)],
      "black"))(21)[c(1, 5, 7, 10, 13, 16, 19) + 1]

SOCdensity  <-
  SOCplotmap(
    data     = density2plot,
    limits   = c(0, 150),
    cols     = cols,
    name     = expression("cropland SOC in tons of carbon per hectare"),
    values   = c(0, 5, 10, 20, 40, 70, 100, 150) / 150,
    breaks   = c(5, 10, 20, 40, 70, 100, 150),
    labels   = c("0     5", "  10", "  20", "  40", "  70", "  100", " >150"))

library(gridExtra)
library(cowplot)

SOCemis
SOCincrease
SOCdensity
SOCshare

grid <- plot_grid(SOCemis, SOCdensity, SOCincrease, SOCshare,
                  ncol = 2, labels = c("(a)", "(b)", "(c)", "(d)"),
                  label_fontface = "plain", label_size = 10)

grid
ggsave(paste0(outputdir, "/4panelfigure.png"),
       plot = grid, width = 20, height = 14, dpi = 300, units = "cm")
ggsave(paste0(outputdir, "/SOCshare.png"),
       plot = SOCshare,    width = 10, height = 7, dpi = 300, units = "cm")
ggsave(paste0(outputdir, "/SOCincrease.png"),
       plot = SOCincrease, width = 10, height = 7, dpi = 300, units = "cm")
ggsave(paste0(outputdir, "/SOCdensity.png"),
       plot = SOCdensity,  width = 10, height = 7, dpi = 300, units = "cm")
ggsave(paste0(outputdir, "/SOCemis.png"),
       plot = SOCemis,     width = 10, height = 7, dpi = 300, units = "cm")
```
